Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-08-01 literature/paper_draft.qmd
expand on introduction section, includeing literature review

To overcome these issues, forecast reconciliation was introduced by @Hyndman2011-jv, and later developed by @Hyndman2016-ic, @Wickramasuriya2019-xq, and others to achieve coherency in point forecasts and enhance accuracy. Forecast reconciliation projects a collection of independent base forecasts into a set of coherent forecasts that respect the linear constraints defining a hierarchical or grouped time-series system.

>>>>

To overcome these issues, forecast reconciliation was introduced by @Hyndman2011-jv, and later developed by @Van_Erven2015-nx, @Hyndman2016-ic, @Ben-Taieb2019-yx, @Wickramasuriya2019-xq, and others to achieve coherency in point forecasts and enhance accuracy. Forecast reconciliation projects a collection of independent base forecasts into a set of coherent forecasts that respect the linear constraints defining a hierarchical or grouped time-series system.

Among the modern reconciliation strategies, the Min Trace (MinT) approach developed by @Wickramasuriya2019-xq is widely used and perform significantly well under right conditions. Despite its properties, MinT relies on a good high-dimensional covariance estimator, which is positive-definite. However, not many researchers have explored this issue in the current literature, except @Carrara2025-rz, who introduced a new estimator for MinT--Double Shrinkage estimator. The current stage of this research piece is fairly early, leaving many potential gaps still not yet to explore. As a result, a study of alternative high-dimensional covariance estimators for MinT is timely and desirable.

The remainder of the paper is organised as follows. @sec-pre-theory provides the basic theoretical framework for hierarchical time series and forecasting, and Min Trace approach, introducing notations, terminologies, and motivations for alternative estimators. @sec-cov-est walks through the main covariance estimators this paper explores, and argues their strengths and weaknesses. @sec-simulation covers the simulation design and currently explores the performance of NOVELIST on MinT. @sec-empirical shows a real-world application of MinT with NOVELIST, which produces results that did not occured in the simulation settings, suggesting further inspection and analysis.
